Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-05-01 ms.tex
switching to pdf figures.
comment out hyperref package.
fixing capitalization of ti file.
Adding Johnson & Quataert to bib file.

\usepackage{amsmath,amssymb}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{hyperref}
\epstopdfsetup{outdir=./figures/}
\graphicspath{{./figures/}}
\usepackage{url}
\usepackage{aas_macros}
\usepackage{astro}
\usepackage{deluxetable}
% \usepackage{natbib}

@@

Equation (\ref{eq:conduction}) shows that, even when
conduction is saturated, our neglect of heat conduction results in at
most an order unity correction for causal values of the saturation
parameter $\phi < 0.1$.  Our numerical experiments which include
conductive heating confirm this ($\S\ref{sec:numerical}$).

% For supersonic inflow, we find that conductivity has little effect on our
% solutions, and our analytics confirm that its effect of redistributing
% heat near the stagnation radius is at most an order unity correction.  We
% do not consider the possibility that the conduction of heat from the very
% inner accretion flow can affect the flow on much larger scales \

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{TI.pdf}
  \caption{Minimum effective wind heating parameter required for
    thermal stability as a function of SMBH mass.  Black lines show
    $v_{\rm TI}$ (eq.~[\ref{eq:cooling3}]), the heating rate required
    for $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} > 10$ in the
    high-heating limit when the stagnation radius lies interior to the
    influence radius, for different values of the mass loss parameter
    $\eta$ as marked.  Blue lines show the minimum heating parameter
    required to have $\zeta > \zeta_c = (r_{b}/r_{\rm
      inf})^{0.5(1-\Gamma)}$ (eq.~[\ref{eq:zetacrit}]), separately for
    cusp (solid) and core (dashed) galaxies. Based on the
    \citet{LauerFaber+:2007a} sample we take $\rinf=25 (8) \Mbh^{0.6}
    pc$ and $\rb=106 \Mbheight^{0.4}$ pc (100 pc)  for cores (cusps). For
    $\zeta < \zeta_c$ the stagnation radius moves from inside the
    influence radius, out to the stellar break radius $r_b$ (Appendix
    \ref{app:be}); in practice renders the flow susceptible to thermal
    runaway, even if $v_{w} > v_{\rm TI}$.  For cusp galaxies the $v_w
    > v_{\rm TI}$ is usually the more strigent criterion for
    stability, while for core galaxies the $\zeta > \zeta_c$ is
    usually more relevant.}
\label{fig:TI}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{profiles.eps}
  \caption{\label{fig:profiles}Radial profiles of the CNM density
    ({\it top}), temperature ({\it middle}), and velocity ({\it
      bottom}), calculated for a representative sample of galaxies.
    Colors denote values of the effective wind heating rate,
    $\vwO=1200$ km s$^{-1}$ ({\it blue}), 600 km s$^{-1}$ ({\it
      orange}), and 300 km s$^{-1}$ ({\it green}).  Line styles denote
    different black hole masses: $\Mbh=10^6 \Msun$ ({\it dot-dashed}),
    $10^7 \Msun$ ({\it solid}), and $10^8 \Msun$ ({\it dashed}). Thin
    and thick lines denote cusp galaxies ($\Gamma$=0.8) and core
    galaxies ($\Gamma$=0.1), respectively.  Squares mark the locations
    of the stagnation radius.  }
\end{figure}

@@

    $    10^{ 6 }$ & 300 & -- & 0.12 & $ 5.1 \times 10^{ -5 }$ & 28 \\

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.eps}
  \caption{\label{fig:stag} Stagnation radius $r_{s}$ in units of the
    sphere of influence radius $r_{\rm inf}$ (eq.~[\ref{eq:rsoi}]) for
    galaxies in our sample as a function of the stellar wind heating
    parameter $\zeta \equiv \sqrt{1+(v_w/\sigma_0)^{2}}$.  Green,
    orange, and blue symbols correspond to different values of $v_{w}
    =$ 300, 600, and 1200 km s$^{-1}$, respectively.  Squares
    correspond to cusp galaxies ($\Gamma = 0.8$), while triangles
    correspond to cores ($\Gamma = 0.1$). Green circles correspond to
    cusp solutions which would be thermally unstable.  The black
    curves correspond to the analytic prediction from equation
    (\ref{eq:rs2main}), with thick solid and dot-dashed curves
    calculated for parameters $(\Gamma=0.8, \densSlope\simeq 1)$ and
    $(\Gamma=0.1,\densSlope\simeq0.6)$, respectively. The thin black
    solid line corresponds to the simplified analytic result for $\rs$
    from equation~\eqref{eq:stag_simple} (recall that $\rinf \simeq 14
    \Mbheight^{0.6} {\rm pc}$).}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{mdot_mass.eps}
  \caption{\label{fig:mdot_mass} Accretion rate $\dot{M}/\dot{M}_{\rm
      edd}$ versus SMBH mass for galaxies in our sample, calculated
    for different values of the wind heating parameter $\vwO =$ 300 km
    s$^{-1}$ ({\it green}), 600 km s$^{-1}$ ({\it orange}), and 1200
    km s$^{-1}$ ({\it blue}).  Squares correspond to cusp galaxies
    ($\Gamma=0.8$), while triangles correspond to cores
    ($\Gamma$=0.1). Green circles correspond to cusp solutions which
    would be thermally unstable.  Thin solid and dot-dashed curves
    correspond to our simple analytic estimates of $\dot{M}/\dot{M}_{\rm
      edd}$ (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies,
    respectively.  Thick curves correspond to the more accurate implicit analytic expression given by equation \eqref{eq:rs2main}.}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{cooling.eps}
  \caption{\label{fig:cooling} Ratio of the rates of heating to
    radiative cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$, as a
    function of radius (solid lines) for a $\Mbh=10^7 \Msun$ cusp
    galaxy ($\Gamma=0.8$).  Dashed lines show the ratio of the cooling
    timescale to the free-fall timescale $t_{\rm cool}/t_{\rm ff}$.
    For high heating rates both ratios are approximately equal at the
    stagnation radius (squares).  When $\dot{q}_{\rm
      heat}/\dot{q}_{\rm rad} \lesssim 10$ (or, equivalently, $t_{\rm
      cool}/t_{\rm ff} \lesssim 10$ near the stagnation radius), then
    the flow is susceptible to thermal instabilities.}
\end{figure}

@@

  \item Including the effects of heat transport by electron conduction
    results in at most order unity changes to the key properties of
    the flow (e.g. stagnation radius, mass accretion rate, and thermal
    stability) for causal values of the conduction saturation
    parameter $\phi < 0.1$ (eq.~[\ref{eq:conduction}]).  Angular
    momentum is also unlikely to invalidate our spherically symmetric
    model on large scales, given observationally inferred rotation
    rates of galactic nuclei near the stagnation radius
    ($\S\ref{sec:rotation}$).

>>>>

\usepackage{amsmath,amssymb}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{epstopdf}
%\usepackage{hyperref}
\epstopdfsetup{outdir=./figures/}
\graphicspath{{./figures/}}
\usepackage{url}
\usepackage{aas_macros}
\usepackage{astro}
\usepackage{deluxetable}
% \usepackage{natbib}

@@

Equation (\ref{eq:conduction}) shows that, even when conduction is
saturated, our neglecting of heat conduction near the stagnation
radius results in at most an order unity correction for causal values
of the saturation parameter $\phi < 0.1$.  Our numerical experiments
which include conductive heating confirm this
($\S\ref{sec:numerical}$).  We do not consider the possibility that
the conduction of heat from the very inner accretion flow can affect
the flow on much larger scales \citep{Johnson+2007}.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{ti.pdf}
  \caption{Minimum effective wind heating parameter required for
    thermal stability as a function of SMBH mass.  Black lines show
    $v_{\rm TI}$ (eq.~[\ref{eq:cooling3}]), the heating rate required
    for $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}} > 10$ in the
    high-heating limit when the stagnation radius lies interior to the
    influence radius, for different values of the mass loss parameter
    $\eta$ as marked.  Blue lines show the minimum heating parameter
    required to have $\zeta > \zeta_c = (r_{b}/r_{\rm
      inf})^{0.5(1-\Gamma)}$ (eq.~[\ref{eq:zetacrit}]), separately for
    cusp (solid) and core (dashed) galaxies. Based on the
    \citet{LauerFaber+:2007a} sample we take $\rinf=25 (8) \Mbh^{0.6}
    pc$ and $\rb=106 \Mbheight^{0.4}$ pc (100 pc)  for cores (cusps). For
    $\zeta < \zeta_c$ the stagnation radius moves from inside the
    influence radius, out to the stellar break radius $r_b$ (Appendix
    \ref{app:be}); in practice renders the flow susceptible to thermal
    runaway, even if $v_{w} > v_{\rm TI}$.  For cusp galaxies the $v_w
    > v_{\rm TI}$ is usually the more strigent criterion for
    stability, while for core galaxies the $\zeta > \zeta_c$ is
    usually more relevant.}
\label{fig:TI}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{profiles.pdf}
  \caption{\label{fig:profiles}Radial profiles of the CNM density
    ({\it top}), temperature ({\it middle}), and velocity ({\it
      bottom}), calculated for a representative sample of galaxies.
    Colors denote values of the effective wind heating rate,
    $\vwO=1200$ km s$^{-1}$ ({\it blue}), 600 km s$^{-1}$ ({\it
      orange}), and 300 km s$^{-1}$ ({\it green}).  Line styles denote
    different black hole masses: $\Mbh=10^6 \Msun$ ({\it dot-dashed}),
    $10^7 \Msun$ ({\it solid}), and $10^8 \Msun$ ({\it dashed}). Thin
    and thick lines denote cusp galaxies ($\Gamma$=0.8) and core
    galaxies ($\Gamma$=0.1), respectively.  Squares mark the locations
    of the stagnation radius.  }
\end{figure}

@@

    $    10^{ 6 }$ & 300 & -- & 0.12 & $ 5.1 \times 10^{ -5 }$ & 28 & 0.6\\

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.pdf}
  \caption{\label{fig:stag} Stagnation radius $r_{s}$ in units of the
    sphere of influence radius $r_{\rm inf}$ (eq.~[\ref{eq:rsoi}]) for
    galaxies in our sample as a function of the stellar wind heating
    parameter $\zeta \equiv \sqrt{1+(v_w/\sigma_0)^{2}}$.  Green,
    orange, and blue symbols correspond to different values of $v_{w}
    =$ 300, 600, and 1200 km s$^{-1}$, respectively.  Squares
    correspond to cusp galaxies ($\Gamma = 0.8$), while triangles
    correspond to cores ($\Gamma = 0.1$). Green circles correspond to
    cusp solutions which would be thermally unstable.  The black
    curves correspond to the analytic prediction from equation
    (\ref{eq:rs2main}), with thick solid and dot-dashed curves
    calculated for parameters $(\Gamma=0.8, \densSlope\simeq 1)$ and
    $(\Gamma=0.1,\densSlope\simeq0.6)$, respectively. The thin black
    solid line corresponds to the simplified analytic result for $\rs$
    from equation~\eqref{eq:stag_simple} (recall that $\rinf \simeq 14
    \Mbheight^{0.6} {\rm pc}$).}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{mdot_mass.pdf}
  \caption{\label{fig:mdot_mass} Accretion rate $\dot{M}/\dot{M}_{\rm
      edd}$ versus SMBH mass for galaxies in our sample, calculated
    for different values of the wind heating parameter $\vwO =$ 300 km
    s$^{-1}$ ({\it green}), 600 km s$^{-1}$ ({\it orange}), and 1200
    km s$^{-1}$ ({\it blue}).  Squares correspond to cusp galaxies
    ($\Gamma=0.8$), while triangles correspond to cores
    ($\Gamma$=0.1). Green circles correspond to cusp solutions which
    would be thermally unstable.  Thin solid and dot-dashed curves
    correspond to our simple analytic estimates of $\dot{M}/\dot{M}_{\rm
      edd}$ (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies,
    respectively.  Thick curves correspond to the more accurate implicit analytic expression given by equation \eqref{eq:rs2main}.}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{cooling.pdf}
  \caption{\label{fig:cooling} Ratio of the rates of heating to
    radiative cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$, as a
    function of radius (solid lines) for a $\Mbh=10^7 \Msun$ cusp
    galaxy ($\Gamma=0.8$).  Dashed lines show the ratio of the cooling
    timescale to the free-fall timescale $t_{\rm cool}/t_{\rm ff}$.
    For high heating rates both ratios are approximately equal at the
    stagnation radius (squares).  When $\dot{q}_{\rm
      heat}/\dot{q}_{\rm rad} \lesssim 10$ (or, equivalently, $t_{\rm
      cool}/t_{\rm ff} \lesssim 10$ near the stagnation radius), then
    the flow is susceptible to thermal instabilities.}
\end{figure}

@@

  \item In the vicinity of the stagnation radius including the effects
    of heat transport by electron conduction results in at most order
    unity changes to the key properties of the flow (e.g. stagnation
    radius, mass accretion rate, and thermal stability) for causal
    values of the conduction saturation parameter $\phi < 0.1$
    (eq.~[\ref{eq:conduction}]). However, in principle heat conduction
    of heat from the very inner accretion flow can affect the flow on
    much larger scales \citep{Johnson+2007}. Angular momentum is also
    unlikely to invalidate our spherically symmetric model on large
    scales, given observationally inferred rotation rates of galactic
    nuclei near the stagnation radius ($\S\ref{sec:rotation}$).
